Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-04-15 publication_materials/ms_rbc.tex
rev2bi

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{del_ra.PNG}
    \caption{Boundary layer height $\delta$ of marginally-stable thermal equilibria. 
    We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}. 
    Plotting on a log-log scale, we find that $\delta$ and $Ra$ obey a power-law relationship. We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$, implying $Ra \propto  \delta^{-3}$ which remains consistent with \cite{Malkus_1954}}
    \label{fig:bl_ra}
\end{figure}

@@

Simulations performed with MSTE initial conditions do not undergo an initial convective transient period,

>>>>

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{del_ra.PNG}
    \caption{Boundary layer height $\delta$ of marginally-stable thermal equilibria. 
    We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}. 
    Plotting on a log-log scale, we find that $\delta$ and $Ra$ obey a power-law relationship. We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ which is consistent with \cite{Malkus_1954, Wen}}
    \label{fig:bl_ra}
\end{figure}

@@

% Simulations performed with MSTE initial conditions do not undergo an initial convective transient period,
